Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-14 paper/paper.tex
wordings

If the {\sc precision} verification returns $\mathit{false}$, then we
increase the precision of \param{I_b}{F_b} and re-start the {\sc
  synthesise} phase with an empty {\sc inputs} set.  Otherwise, we
found a full sound solution for our synthesis problem and we are done.

@@

Using an optimisation tool, the authors
of~\cite{DBLP:conf/hybrid/WangGRJF16} have designed a high-performance
controller for this plant, which is characterised by the following
$z$-domain transfer function:
%
\begin{equation}
\label{Eq:running-example-controller}
C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation}
%
The authors claim that this controller $C(z)$
(Eq.~\eqref{Eq:running-example-controller}) stabilizes the closed-loop
system for the discrete plant model $G(z)$
(Eq.~\ref{Eq:running-example-plant}).  However, if the effects of finite
precision arithmetic are considered during verification (e.g., fixed-point
arithmetic and word-length), then this closed-loop system becomes unstable.
%
For instance, an implementation of $C(z)$ using \param{4}{16} fixed-point
numbers (i.e., $4$ bits for the integer part and $16$ bits for the
fractional part) can be modeled as follows:
%
\begin{equation}
\label{Eq:running-example-controller-quantised}
C_{q}\left(z\right) {:=} \frac{2.719986z^2{-}4.153000z
{+}1.895996}{z^2{-}1.843994z+0.849594} \;.
\end{equation} 
%
The resulting system using the typical series loop configuration, where
$C_{q}\left(z\right)$ and $G\left(z\right)$ are in the forward path, is
unstable.

@@

We will illustrate our synthesis approach on the running example
described in the previous section. 
%in Sec.~\ref{sec:running-ex}.
We start with the candidate solution with all coefficients zero 
given below at $I_b=16,F_b=24$.
Note that the digital controller is designed with typical control system
techniques \cite{Kuo:2002:ACS:579453,Ogata:1987:DCS:26170}.
%
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.
%
%$$
%\begin{array}{ll}
%N_C(z) {=} 0z^2{+}0z{+}0\\
%D_C(z) {=} 0z^2{+}0z{+}0\\
%\end{array}
%$$
$$
C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0}
$$

@@

We add this counterexample to {\sc inputs} and initiate the {\sc synthesise}
phase, where we get the following candidate solution:
%
%\red{[ How is the order of the candidate solution chosen here?]}
$$
C(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}
$$

This time, the {\sc uncertainty} check does not find any more
counterexamples and we pass the current candidate solution to the {\sc
precision} verification stage.
%
% In the second {\sc verify} phase, we check whether the current candidate
% solution above is the final solution. It is not and the verifier signals
% that it is due to lack of precision.
%
We obtain the result $\mathit{false}$, meaning that the current precision is
insufficient.  Consequently, we increase our precision to $I_b=20$, $F_b=28$.
%
Since the previous counterexamples were obtained at lower precision, we
remove them from the counterexample set.  Back in the {\sc synthesise}
phase, we re-start the process with a candidate solution with all
coefficients $0$.  Next, the {\sc uncertainty} verification stage provides
the first counterexample at higher precision:
%
%$$
%\begin{array}{ll}
%\Delta N_G(z) {=} 0.026314\\
%\Delta D_G(z) {=} 0.999024z{-}1.004785
%\end{array}
%$$
$$
\tilde G(z) = \frac{0.026314}{0.999024z{-}1.004785}
$$

@@

This candidate solution is validated as the final solution by both stages 
{\sc uncertainty} and {\sc precision} in the
{\sc verify} phase. %, which fails to find a new counterexample (i.e. returns UNSAT).

>>>>

If the {\sc precision} verification returns $\mathit{false}$, then we
increase the precision of \param{I_b}{F_b} and re-start the {\sc synthesise}
phase with an empty {\sc inputs} set.  Otherwise, we found a full solution
for our synthesis problem and we are done.

@@

Using an optimisation tool, the authors
of~\cite{DBLP:conf/hybrid/WangGRJF16} have designed a high-performance
controller for this plant, which is characterised by the following
$z$-domain transfer function:
%
\begin{equation}
\label{Eq:running-example-controller}
C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation}
%
The authors of~\cite{DBLP:conf/hybrid/WangGRJF16} claim that this controller
$C(z)$ (Eq.~\eqref{Eq:running-example-controller}) stabilizes the
closed-loop system for the discrete plant model $G(z)$
(Eq.~\ref{Eq:running-example-plant}).  However, if the effects of finite
precision arithmetic are considered during verification (e.g., fixed-point
arithmetic and word-length), then this closed-loop system becomes unstable.
%
For instance, an implementation of $C(z)$ using \param{4}{16} fixed-point
numbers (i.e., $4$ bits for the integer part and $16$ bits for the
fractional part) can be modeled as follows:
%
\begin{equation}
\label{Eq:running-example-controller-quantised}
C_{q}\left(z\right) {:=} \frac{2.719986z^2{-}4.153000z
{+}1.895996}{z^2{-}1.843994z+0.849594} \;.
\end{equation} 
%
The resulting system using the typical series loop configuration, where
$C_{q}\left(z\right)$ and $G\left(z\right)$ are in the forward path, is
unstable.

@@

We now demonstrate how our approach solves the synthesis problem for the
example given in the previous section.  We start with the candidate solution
with all coefficients zero, as given below, and a precision of $I_b=16$,
$F_b=24$.  The digital controller is designed with standard techniques for
control systems~\cite{Kuo:2002:ACS:579453, Ogata:1987:DCS:26170}.
%
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.
%
%$$
%\begin{array}{ll}
%N_C(z) {=} 0z^2{+}0z{+}0\\
%D_C(z) {=} 0z^2{+}0z{+}0\\
%\end{array}
%$$
$$ C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0} $$

@@

We add this counterexample to {\sc inputs} and initiate the {\sc synthesise}
phase, where we obtain the following candidate solution:
%
%\red{[ How is the order of the candidate solution chosen here?]}
$$
C(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}
$$

This time, the {\sc uncertainty} check does not find any
counterexample and we pass the current candidate solution to the {\sc
precision} verification stage.
%
% In the second {\sc verify} phase, we check whether the current candidate
% solution above is the final solution. It is not and the verifier signals
% that it is due to lack of precision.
%
We obtain the result $\mathit{false}$, meaning that the current precision is
insufficient.  Consequently, we increase our precision to $I_b=20$, $F_b=28$.
%
Since the previous counterexamples were obtained at lower precision, we
remove them from the set of counterexamples.  Back in the {\sc synthesise}
phase, we re-start the process with a candidate solution with all
coefficients $0$.  Next, the {\sc uncertainty} verification stage provides
the first counterexample at higher precision:
%
%$$
%\begin{array}{ll}
%\Delta N_G(z) {=} 0.026314\\
%\Delta D_G(z) {=} 0.999024z{-}1.004785
%\end{array}
%$$
$$ \tilde G(z) = \frac{0.026314}{0.999024z{-}1.004785} $$

@@

This candidate solution is validated as the final solution by both stages
{\sc uncertainty} and {\sc precision} in the {\sc verify} phase.

%, which fails to find a new counterexample (i.e. returns UNSAT).
